A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-31 03_Prep_data.Rmd
Small edits Move final check plots for better flow Add some more headings

There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit. 
However, seven treatments are missing Mean square error.

@@

```{r}
hist_usq(PM_MB_dat$grain_yield.t.ha, main = "Grain yield (t / ha)")
hist_usq(log(PM_MB_dat$grain_yield.t.ha), main = "log(Grain yield (t / ha))")
hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha), main = "sqrt(Grain yield (t / ha))")
hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)")
```
The distribution of data does not seem to be improved by transformation of the data.
We will retain the continuous variable grain_yield.t.ha as the response.
Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.

@@

```{r MSE_2_SVar}
#calculation when using log of response
# PM_MB_dat$vi <-
#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha ^
#                                   2)

@@

These categorical variables are named:

   - **Early**: First fungicide application was prior to first sign of disease. 
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

There are few 'Early_plus' treatments, these treatments therefore will have too few comparisons with other treatments in the meta-analysis to provide accurate results. Therefore we will remove 'Early_plus' from the analysis.

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus")
```

Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?

****

@@

>>>>

There is a somewhat better trend here, if sampling variance from standard deviation proves unsuitable for the analysis we may compare models using variance from stdev and mean square for the best fit. 
However, seven treatments are missing mean square error.

@@

```{r}
hist_usq(PM_MB_dat$grain_yield.t.ha., main = "Grain yield (t / ha)")
hist_usq(log(PM_MB_dat$grain_yield.t.ha.), main = "log(Grain yield (t / ha))")
hist_usq(sqrt(PM_MB_dat$grain_yield.t.ha.), main = "sqrt(Grain yield (t / ha))")
hist_usq(PM_MB_dat$yield_gain, main = "Mean difference to control (t / ha)")
```

The distribution of data does not seem to be improved by transformation of the data.
We will retain the continuous variable grain_yield.t.ha as the response.
Mean differences won't be used as we are following the methodology of a ARM-based model, where mean differences are calculated following the meta-analysis.

@@

```{r MSE_2_SVar}
#calculation when using log of response
# PM_MB_dat$vi <-
#    PM_MB_dat$Y_Msquare / (PM_MB_dat$n * PM_MB_dat$grain_yield.t.ha. ^
#                                   2)

@@

These categorical variables are named:
   - **Early**: First fungicide application was prior to first sign of disease. 
   - **Recommended**: First fungicide application was applied on the day powdery mildew was observed, or within three days of first sign. 
   - **Late**: First fungicide application was four or more days after first sign of disease being observed.

@@

'Early_plus' treatments are few in number, these treatments will have too few comparisons with other treatments in the meta-analysis to provide accurate results. Therefore we will remove 'Early_plus' from the analysis.

```{r simpler_clusters_remove}
PM_MB_dat <-
   PM_MB_dat %>%
   filter(spray_management != "Early_plus")
```
*****

@@

## Final data check  
Now we have defined our treatments lets inspect plots to visualise how well the data compares across the trial years and locations?

### Simplify and save data
